File-based localization of numerical perturbations in data analysis pipelines

### 2020-07-22 paper.tex

%%%% Commands %%%%
% \newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
% \newcommand{\note}[2]{\color{blue}Note from \textsc{#1}: #2\color{black}}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\toolname}[0]{Spot\xspace}
\newcommand{\flirt}[0]{\texttt{flirt}\xspace}
\newcommand{\fnirt}[0]{\texttt{fnirt}\xspace}

@@

\begin{abstract} 
Data analysis pipelines are known to be impacted by computational conditions, presumably due to the creation,
propagation, and amplification of numerical errors. While this process could
play a major role in the current reproducibility crisis, the precise
causes of such instabilities and the path along which they propagate in
pipelines are unclear. We present \toolname, a tool to identify which
processes in a pipeline create numerical differences
when executed in different computational conditions. \toolname
leverages system-call interception through \reprozip to reconstruct and compare provenance
graphs without pipeline instrumentation. By applying \toolname to the
structural pre-processing pipelines of the Human Connectome
Project, we found that linear and non-linear registration are the cause of
most numerical instabilities in these pipelines, which confirms previous
findings.
\end{abstract}

@@

\begin{figure*}
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.9\linewidth]{figures/p-graph.pdf}
    \caption{Raw provenance graph (\reprozip output), with transient files shown in gray boxes.}
    \label{fig:provenance-graph}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{figures/p-graph-dag.pdf}
    \caption{Provenance DAG, with disambiguated transient files.}
    \label{fig:provenance-dag}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
      \centering
      \includegraphics[width=.7\linewidth]{figures/p-graph-dag-labelled.pdf}
     \caption{Labeled DAG comparing 2 execution conditions, showing 1 non-reproducible process.}
     \label{fig:labeled-dag} 
  \end{subfigure}
    % \includegraphics[width=.8\columnwidth]{figures/provenance-graphs}
    \caption{Provenance graphs created from the example pipeline in
    Listing~\ref{listing:sample-script}. Processes are represented with
    circles, files with rectangles, and read/write accesses with plain edges. For convenience, the process tree 
    is also shown, with gray dashed edges. Processes forked by
    \texttt{bet} were captured by \reprozip while they did not appear in
    Listing~\ref{listing:sample-script}. Processed associated with
    executables located in \texttt{/usr/bin/} or \texttt{/bin/} are not shown.
  }
    \label{fig:spot-example}
  \end{figure*}

@@

\begin{listing}
  \inputminted{bash}{"data/example/example.sh"}
  \caption{Example pipeline}
  \label{listing:sample-script}
\end{listing}

@@

@@

We processed the 20 subjects with PreFreeSurfer and FreeSurfer, using the 2
CentOS versions. Each subject was processed twice on the same operating
system to detect within-OS variability coming from pseudo-random
operations. We compared pipeline results using  FreeSurfer tools \texttt{mri\_diff},
\texttt{mris\_diff}, and \texttt{lta\_diff}, to ignore execution-specific information such as file path or
timestamps. To compare segmentations $X$ and $Y$, we used the Dice coefficient defined as follows:
\[DICE=\frac{2|X \cap Y|}{|X| + |Y|}\]

@@

\section{Results}

The average processing time per subject was approximately 2~hours for
PreFreeSurfer and 8~hours for FreeSurfer. The average output file size was
2.7~GB for PreFreeSurfer and 4.1~GB for FreeSurfer.
%\tristan{Ali, are these numbers per subject or for 20 subjects? it's an average of 20 subjects}
For each subject, PreFreeSurfer accessed
83K files and created 7.7K processes, and FreeSurfer accessed 62K files and 
created 4K processes.

% \subsection{Subject clustering}

@@

Figure~\ref{fig:pfs_heatmap} shows the frequency of non-reproducible pipeline processes
in PreFreeSurfer. 
The processes identified as non-reproducible were observed in linear registration 
with FSL \flirt (in ACPC-Alignment, Brain Extraction, Distortion Correction, and
Atlas Registration), in non-linear registration with FSL \fnirt (in Brain Extraction 
and Atlas Registration), and in image warping with FSL \texttt{new\_invwarp} (in Brain Extraction 
and Atlas Registration). Differences were also observed in image mean 
computations with FSL \texttt{maths}  (in Anatomical Average). 
Figure~\ref{fig:complete_pfs} shows a complete PreFreeSurfer labeled DAG, localizing 
the observed differences in the entire pipeline, for a given subject.
\begin{figure*}
\centering
  \includegraphics[width=\textwidth]{./figures/heatmap.pdf}
  \caption{Heatmap of non-reproducible processes across PreFreeSurfer pipeline steps.
  Each cell represents the occurrence of a particular command line in a
  pipeline step among Anatomical Average (AAve), Anterior/Posterior
  Commissure Alignment (ACPC-A), Brain Extraction (BExt), Bias Field
  Correction (BFC), or Atlas-Registration (AR). Cell labels indicate the
  fraction of subjects for which the corresponding process wasn't reproducible. For example,
  the \flirt tool was invoked 6 times in step DC for each of the 20
  subjects: 2 instances weren't reproducible in 19 subjects, 3
  instances were always reproducible, and 1 instance wasn't reproducible in
  17 subjects. }
  \label{fig:pfs_heatmap}
\end{figure*}

\begin{figure*} 
   \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline. For better visualization, processes associated with commands 
    in \texttt{/bin} or \texttt{/usr/bin} were ommitted, as well as 
  \texttt{imtest}, \texttt{imcp}, \texttt{remove\_ext}, \texttt{fslval}, \texttt{avscale}, and \texttt{fslhd}.}
    \label{fig:complete_pfs}
\end{figure*}

To illustrate the magnitude of the differences,
Figure~\ref{fig:fnirt_result} compares \fnirt results in Brain Extraction
for a particular subject. Differences appear to be important, in
particular in the areas framed in red.
\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{figures/t2w_alignment.png} 
    \caption{Differences between T2 \fnirt results in PreFreeSurfer's Brain Extraction (CentOS6 vs 
    CentOS7). An animated version of the comparison is available \href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/figures/pfs_t2w_alignment.gif}{here}.}
    \label{fig:fnirt_result}
\end{figure}

@@

However, FreeSurfer results still differ between conditions, due to the
propagation and amplification of differences created in PreFreeSurfer. We
observed the effect of this propagation in FreeSurfer results, as shown in
Figure~\ref{fig:tissue_class} for whole-brain segmentations. The
Dice coefficients associated with the 44 regions segmented by
FreeSurfer are shown in Figure~\ref{fig:scatter_plot}, showing that Dice coefficents below 0.9 are 
observed in most regions, and particularly in the smallest ones.
\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{figures/brain_segmentation_mni.png} 
  \caption{Sum of binarized differences between whole-brain FreeSurfer
  segmentations obtained from PreFreeSurfer processings in CentOS6 vs CentOS7
   (N=20). Segmentations were resampled and overlaid to the MNI152 volume
  template. An animated comparison of segmentations obtained for a particular subject is available
\href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/figures/fs_brain_segmentation.gif}
{here}.
} 
  \label{fig:tissue_class}
\end{figure}

\begin{figure*}
  \hspace*{-1cm}
  \includegraphics[width=1.1\linewidth]{figures/dice_regions.pdf}
    \caption{Dice coefficients between regions segmented by FreeSurfer in CentOS6 vs CentOS7 (N=20), ordered by increasing 
    median values. Boxes brightness is proportional to the logarithm of the corresponding brain region size.}
    \label{fig:scatter_plot}
  \end{figure*}

@@

>>>>

%%%% Commands %%%%
% \newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
% \newcommand{\note}[2]{\color{blue}Note from \textsc{#1}: #2\color{black}}
\newcommand{\revision}[1]{\color{purple}\textbf{REVISION:}#1\color{black}}
\newcommand{\revised}[1]{\color{blue}\textbf{REVISED:}#1\color{black}}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\toolname}[0]{Spot\xspace}
\newcommand{\flirt}[0]{\texttt{flirt}\xspace}
\newcommand{\fnirt}[0]{\texttt{fnirt}\xspace}

@@

\begin{abstract} 
Data analysis pipelines are known to be impacted by computational conditions, presumably due to the creation 
and propagation of numerical errors. While this process could
play a major role in the current reproducibility crisis, the precise
causes of such instabilities and the path along which they propagate in
pipelines are unclear. We present \toolname, a tool to identify which
processes in a pipeline create numerical differences
when executed in different computational conditions. \toolname
leverages system-call interception through \reprozip to reconstruct and compare provenance
graphs without pipeline instrumentation. By applying \toolname to the
structural pre-processing pipelines of the Human Connectome
Project, we found that linear and non-linear registration are the cause of
most numerical instabilities in these pipelines, which confirms previous
findings.
\end{abstract}

@@

\revised{
The labeled graph can be different depending on the condition that we obtained \reprozip trace as it can produce 
different DAGs. Even using the same DAGs, it depends on the order of executions in which condition 
we execute pipeline to pinpoint the propagation of differences. 
Therefore, any permutation of these two factors can produce different results.
% Pinpointing differences in one condition can be different than other condition.

% add a paragraph to the methods, to explain that the order matters, due to:
% 1. possible differences in the reprozip trace
% 2. the way the comparison is done
}

\begin{figure*}
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.9\linewidth]{figures/p-graph.pdf}
    \caption{Raw provenance graph (\reprozip output), with transient files shown in gray boxes.}
    \label{fig:provenance-graph}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{figures/p-graph-dag.pdf}
    \caption{Provenance DAG, with disambiguated transient files.}
    \label{fig:provenance-dag}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
      \centering
      \includegraphics[width=.7\linewidth]{figures/p-graph-dag-labelled.pdf}
     \caption{Labeled DAG comparing 2 execution conditions, showing 1 non-reproducible process.}
     \label{fig:labeled-dag} 
  \end{subfigure}
    % \includegraphics[width=.8\columnwidth]{figures/provenance-graphs}
    \caption{Provenance graphs created from the example pipeline in
    Listing~\ref{listing:sample-script}. Processes are represented with
    circles, files with rectangles, and read/write accesses with plain edges. For convenience, the process tree 
    is also shown, with gray dashed edges. Processes forked by
    \texttt{bet} were captured by \reprozip while they did not appear in
    Listing~\ref{listing:sample-script}. Processed associated with
    executables located in \texttt{/usr/bin/} or \texttt{/bin/} are not shown.
    \revised{Node labels are enlarged.}}
    \label{fig:spot-example}
  \end{figure*}

@@

\begin{listing}
  \inputminted{bash}{"data/example/example.sh"}
  \caption{\revised{Example pipeline: computes the volume and number 
  of voxels of the brain from a T1 image.}}
  \label{listing:sample-script}
\end{listing}

@@

\subsection{Implementation}
\revised{ 
The tool is implemented in Python programming language and supports the Python version 3.5 and higher.
It utilizes the Python modules including NumPy~\cite{oliphant2006guide} and Pandas~\cite{mckinney2011pandas}, 
which allow data processing, 
SciPy~\cite{2020SciPy-NMeth} and Scikit-learn~\cite{pedregosa2011scikit} packages 
for clustering the subjects, and Zss~\cite{zhang1989simple} package to calculate the tree distances.
Also, the Python APIs of Docker and Boutiques~\cite{glatard2018boutiques} tools were used to create the container 
images and simplify the pipeline executions.

We used the latest version of Boutiques tool v0.5.25 for creating descriptors 
to execute pipelines across the operating systems automatically.
In a JSON schema, the descriptors define inputs, outputs, error codes, containers, and the command line for running pipelines.

Besides, we used \reprozip tool version 1.0.16 to collect the pipeline system call processes and 
files in an SQLite file format.
}

@@

We processed the 20 subjects with PreFreeSurfer and FreeSurfer, using the 2
CentOS versions. 
\revised{Using the \reprozip trace obtained from CentOS7, 
we captured transient files in CentOS6 and labeled pipeline processes in CentOS7.}
Each subject was processed twice on the same operating
system to detect within-OS variability coming from pseudo-random
operations. We compared pipeline results using  FreeSurfer tools \texttt{mri\_diff},
\texttt{mris\_diff}, and \texttt{lta\_diff}, to ignore execution-specific information such as file path or
timestamps. To compare segmentations $X$ and $Y$, we used the Dice coefficient defined as follows:
\[DICE=\frac{2|X \cap Y|}{|X| + |Y|}\]

\revised{
The Dice coefficient~\cite{dice1945measures} is a commonly used metric in validating medical image segmentation.
The Dice value ranges from 0 to 1, with 1 indicating a complete overlap between two segmentation results.
Besides, the Jaccard coefficient~\cite{jaccard1912distribution} can be considered an equivalent metric 
to measure the overlap between images.

% Also, we used the Pearson correlation coefficient to establish the relationship between Dice value and segmented region size.
% Like other correlation coefficients, this one varies between -1 and +1 with 0 implying no correlation. 
% Correlations of -1 or +1 imply an exact linear relationship. 
}

@@

\section{Results}
\revised{
All experiments were run on the machine with a 3.4GHz Intel Core i7 processor 
and 32GB memory under the CentOS7 operating system.
The average processing time per subject was approximately 2~hours for
PreFreeSurfer and 8~hours for FreeSurfer. The average output file size was
2.7~GB for PreFreeSurfer and 4.1~GB for FreeSurfer.
%\tristan{Ali, are these numbers per subject or for 20 subjects? it's an average of 20 subjects}
For each subject, PreFreeSurfer accessed
83K files and created 7.7K processes, and FreeSurfer accessed 62K files and 
created 4K processes.
The scripts and analyses used to create the figures in this section are available at 
\url{https://github.com/big-data-lab-team/HCP-reproducibility-paper}.
}
% \subsection{Subject clustering}

@@

Figure~\ref{fig:pfs_heatmap} shows the frequency of non-reproducible pipeline processes
in PreFreeSurfer. 
The processes identified as non-reproducible were observed in linear registration 
with FSL \flirt (in ACPC-Alignment, Brain Extraction, Distortion Correction, and
Atlas Registration), in non-linear registration with FSL \fnirt (in Brain Extraction 
and Atlas Registration), and in image warping with FSL \texttt{new\_invwarp} (in Brain Extraction 
and Atlas Registration). Differences were also observed in image mean 
computations with FSL \texttt{maths}  (in Anatomical Average). 
Figure~\ref{fig:complete_pfs} shows a complete PreFreeSurfer labeled DAG, localizing 
the observed differences in the entire pipeline, for a given subject.
\begin{figure*}
\centering
  \includegraphics[width=\textwidth]{./figures/heatmap.pdf}
  \caption{Heatmap of non-reproducible processes across PreFreeSurfer pipeline steps.
  Each cell represents the occurrence of a particular command line in a
  pipeline step among Anatomical Average (AAve), Anterior/Posterior
  Commissure Alignment (ACPC-A), Brain Extraction (BExt), Bias Field
  Correction (BFC), or Atlas-Registration (AR). Cell labels indicate the
  fraction of subjects for which the corresponding process wasn't reproducible. For example,
  the \flirt tool was invoked 6 times in step DC for each of the 20
  subjects: 2 instances weren't reproducible in 19 subjects, 3
  instances were always reproducible, and 1 instance wasn't reproducible in
  17 subjects. 
  \revised{Grey cells show that any command line of the process did not occur in the pipeline step.}}
  \label{fig:pfs_heatmap}
\end{figure*}

\begin{figure*} 
   \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline. 
    \revised{Node labels show the same abbreviations as in Figure~\ref{fig:pfs_heatmap}.}
    For better visualization, processes associated with commands 
    in \texttt{/bin} or \texttt{/usr/bin} were omitted, as well as 
  \texttt{imtest}, \texttt{imcp}, \texttt{remove\_ext}, \texttt{fslval}, \texttt{avscale}, and \texttt{fslhd}.}
    \label{fig:complete_pfs}
\end{figure*}

\revised{
Figure~\ref{fig:fnirt_result} compares \fnirt results in Brain Extraction
for a particular subject using the checkerboard pattern.
Differences appear to be visually important, in particular in the areas framed in red.
The checkerboard representation is a common method to illustrate the magnitude of the differences in registration results.
Although differences are more clearly represented in the animations linked in this figure.}

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{figures/t2w_alignment.png} 
    \caption{Differences between T2 \fnirt results in PreFreeSurfer's Brain Extraction (CentOS6 vs 
    CentOS7). 
    \revised{
    The colored squares indicate result images obtained from CentOS6 (in purple) and CentOS7 (in green), 
    and the red boxes highlight regions with significant differences.}
    % Result images obtained from CentOS6 and CentOS7 are colored in purple and green squares.
    % The red boxes highlight regions with significant differences.}
    An animated version of the comparison is available \href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/figures/pfs_t2w_alignment.gif}{here}.}
    \label{fig:fnirt_result}
\end{figure}

@@

However, FreeSurfer results still differ between conditions, due to the
propagation of differences created in PreFreeSurfer. We
observed the effect of this propagation in FreeSurfer results, as shown in
Figure~\ref{fig:tissue_class} for whole-brain segmentations. The
Dice coefficients associated with the 44 regions segmented by
FreeSurfer are shown in Figure~\ref{fig:scatter_plot}, showing that Dice coefficents below 0.9 are 
observed in most regions, and particularly in the smallest ones.
\revised{
The correlation between the Dice values and region sizes computed as the Pearson's correlation coefficient 
was 0.12 (\emph{P}=.43). 
The positive correlation implies that as region size increases, Dice value increases. 
% This is an average Dice values over 20 subjects for each 44 regions.
}

\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{figures/brain_segmentation_mni.png} 
  \caption{Sum of binarized differences between whole-brain FreeSurfer
  segmentations obtained from PreFreeSurfer processings in CentOS6 vs CentOS7
   (N=20). Segmentations were resampled and overlaid to the MNI152 volume
  template. 
  \revised{Each voxel shows the number of subjects that created different results. 
  The color bar ranges from 1 to 7 as the minimum and the maximum number of subjects in each voxel.
  Voxels are not colored if the identical results were produced in all 20 subjects.}
  An animated comparison of segmentations obtained for a particular subject is available
\href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/figures/fs_brain_segmentation.gif}
{here}.} 
  \label{fig:tissue_class}
\end{figure}

\begin{figure*}
  \hspace*{-1cm}
  \includegraphics[width=1.1\linewidth]{figures/dice_regions.pdf}
    \caption{Dice coefficients between regions segmented by FreeSurfer in CentOS6 vs CentOS7 (N=20), ordered by increasing 
    median values. 
    \revised{Each point indicates the Dice value in a particular region for a single subject.}
    Boxes brightness is proportional to the logarithm of the corresponding brain region size.}
    \label{fig:scatter_plot}
  \end{figure*}

@@

\revision{
Discuss irreproducibility in 2 parts:
1. code coverage 
2. statistics, see eq 1 in https://ieeexplore.ieee.org/abstract/document/7152570
}

### 2020-07-22 supplementary-files/file1.tex

We used unprocessed data from 20 subjects from the HCP data releases of the 1200 Subject project available in \href{https://db.humanconnectome.org}{the ConnectomDB repository}.
Table \ref{tab:dataset} shows a summary of the subjects.

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{\bf Summary of the subjects used in the experiments.}
\begin{tabular}{ccccc}
\hline
Subject & Release\tnote{1} & Acquisition\tnote{2} & Gender & Age \\
\hline
101309 & S500 & Q06 & M & 26-30 \\
102008 & S500 & Q06 & M & 22-25 \\ 
102311 & S500 & Q06 & F & 26-30 \\
103414 & Q2 & Q02 & F & 22-25 \\
103515 & Q1 & Q02 & F & 26-30 \\
103818 & Q1 & Q01 & F & 31-35 \\
105014 & S500 & Q05 & F & 26-30 \\
105115 & Q2 & Q02 & M & 31-35 \\
106319 & Q3 & Q03 & M & 26-30 \\
106521 & S500 & Q06 & F & 26-30 \\
107321 & S500 & Q04 & F & 22-25 \\
107422 & S500 & Q07 & M & 22-25 \\
108121 & S500 & Q04 & F & 26-30 \\
108323 & S500 & Q04 & F & 26-30 \\
113922 & S500 & Q04 & M & 31-35 \\
140420 & Q2 & Q02 & F & 26-30 \\
140824 & Q3 & Q04 & M & 31-35 \\
140925 & S500 & Q04 & F & 22-25 \\
142424 & Q3 & Q03 & M & 26-30 \\
142828 & Q1 & Q01 & M & 31-35 \\
\hline
\end{tabular}
  \label{tab:dataset}
  \begin{tablenotes}
  \footnotesize
    \item[1] Release refers to the HCP data release in which this subject's data was initially published to ConnectomeDB such as the initial Quarter releases (Q1, Q2, Q3)
    \item[2] Acquisition indicates the Quarter in which this subject's data was initially acquired
  \end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

We used unprocessed data from 20 subjects from the HCP data releases of the 1200 Subject project available in \href{https://db.humanconnectome.org}{the ConnectomeDB repository}.
Table \ref{tab:dataset} shows a summary of the subjects.

\begin{table}[htbp]
\centering
\begin{threeparttable}
\caption{\bf Summary of the subjects used in the experiments.}
\begin{tabular}{ccccc}
\hline
Subject & Release\tnote{1} & Acquisition\tnote{2} & Gender & Age \\
\hline
101309 & S500 & Q06 & M & 26-30 \\
102008 & S500 & Q06 & M & 22-25 \\ 
102311 & S500 & Q06 & F & 26-30 \\
103414 & Q2 & Q02 & F & 22-25 \\
103515 & Q1 & Q02 & F & 26-30 \\
103818 & Q1 & Q01 & F & 31-35 \\
105014 & S500 & Q05 & F & 26-30 \\
105115 & Q2 & Q02 & M & 31-35 \\
106319 & Q3 & Q03 & M & 26-30 \\
106521 & S500 & Q06 & F & 26-30 \\
107321 & S500 & Q04 & F & 22-25 \\
107422 & S500 & Q07 & M & 22-25 \\
108121 & S500 & Q04 & F & 26-30 \\
108323 & S500 & Q04 & F & 26-30 \\
113922 & S500 & Q04 & M & 31-35 \\
140420 & Q2 & Q02 & F & 26-30 \\
140824 & Q3 & Q04 & M & 31-35 \\
140925 & S500 & Q04 & F & 22-25 \\
142424 & Q3 & Q03 & M & 26-30 \\
142828 & Q1 & Q01 & M & 31-35 \\
\hline
\end{tabular}
  \label{tab:dataset}
  \begin{tablenotes}
  \footnotesize
    \item[1] Release refers to the HCP data release in which this subject's data was initially published to ConnectomeDB
    \item[2] Acquisition indicates the Quarter in which this subject's data was initially acquired
  \end{tablenotes}
\end{threeparttable}
\end{table}
